\chapter{Discussion}
\section{Overview}
Start with a few sentences that summarize the most important results. The discussion section should be a brief essay in itself, answering the following questions and caveats:
\begin{itemize}
  \item What are the major patters in the observations? (refer to spatial and temporal variations.)
  \item What are the relationships, trends and generalizations among the results?
  \item What are the exceptions to these patterns or generalizations?
  \item What are the likely causes (mechanisms) underlying these patterns resulting predictions?
  \item Is there agreement or disagreement with previous work?
  \item Interpret results in terms of background laid out in the introduction - what is the relationship of the present results to the original question?
  \item What is the implication of the present results for other unanswered questions in earth sciences, ecology, environmental policy, etc...?
  \item Multiple hypotheses: There are usually several possible explanations for results. Be careful to consider all of these rather than simply pushing your favorite one. If you can eliminate all but one, that is great, but often that is not possible with the data in hand. In that case you should give even treatment to the remaining possibilities, and try to indicate ways in which future work may lead to their discrimination.
  \item Avoid bandwagons: A special case of the above. Avoid jumping a currently fashionable point of view unless your results really do strongly support them.
  \item What are the things we now know or understand that we didn't know or understand before the present work?
  \item Include evidence or line of reasoning supporting each interpretation.
  \item What is the significance of the present results: why should we care?
\end{itemize}
This section should be rich in references to similar work and background needed to interpret results. However, interpretation/discussion section(s) are often too long and verbose. Is there material that doesn't contribute to one of the elements listed above? If so, this may be material that you will want to consider deleting or moving. Break up section into logical segments by using subheads.
\input{./Discussion/RampWing/RampWing.tex}
\input{./Discussion/SweptUnswept/SweptUnswept.tex}
\input{./Discussion/Vane/Vane.tex}


