\chapter{Introduction}
You can't write a good introduction until you know what the body of the paper says. Consider writing the introductory section(s) after you have completed the rest of the paper, rather than before.
Be sure to include a hook at the beginning of the introduction. This is a statement of something sufficiently interesting to motivate your reader to read the rest of the paper, it is an important/interesting scientific problem that your paper either solves or addresses. You should draw the reader in and make them want to read the rest of the paper.

The next paragraphs in the introduction should cite previous research in this area. It should cite those who had the idea or ideas first, and should also cite those who have done the most recent and relevant work. You should then go on to explain why more work was necessary (your work, of course.) 
 
What else belongs in the introductory section(s) of your paper? 
\begin{enumerate}
 \item A statement of the goal of the paper: why the study was undertaken, or why the paper was written. Do not repeat the abstract.
 \item Sufficient background information to allow the reader to understand the context and significance of the question you are trying to address.
 \item Proper acknowledgment of the previous work on which you are building. Sufficient references such that a reader could, by going to the library, achieve a sophisticated understanding of the context and significance of the question.
 \item The introduction should be focused on the thesis question(s). All cited work should be directly relevant to the goals of the thesis. This is not a place to summarize everything you have ever read on a subject.
 \item Explain the scope of your work, what will and will not be included.
 \item A verbal ``road map'' or verbal ``table of contents'' guiding the reader to what lies ahead.
 \item Is it obvious where introductory material (``Old stuff'') ends and your contribution (``new stuff'') begins?
\end{enumerate}
Remember that his is not a reviewer paper. We are looking for original work and interpretation/analysis by you. Break up the introduction section into logical segments by using subheads.
